---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

Wilson et. al. suggest to keep track of changes.  They say to keeo changes small and save changes frequently and make notes of who made the changes.  This is important because sometimes the changes may be incorrect or an earlier verson was better.  It is important to know when and where the changes were made to the code or the document.  They suggest making a folder for each project and having a CHANGELOG.txt in the folder to note who, what, and when was changed in the project and to copy the whole document when large changes are being made to have a before and after version of the change.  Most importantly keep track of the versions of the project.  This is important because analysis on version1 will likely be different than analysis on version12. 

3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 


4) Push this homework to the GitHub repository for the homework. 


```{r}
(sqrt(4))^13

```



